An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-21 Revision/response.tex

\myfbox{
	\begin{weakness}
		\textit{In the experimental setup, it is unclear whether data storage (disk or SSD) is used.
			In Table 1, please clarify which methods are disk-based, and which methods are memory-based.
			For disk-based methods, it is also meaningful to report the cost breakdown (e.g., in terms of I/O time and CPU time).}
	\end{weakness}
}

\noindent
\textbf{Response:} 
Thank you for your suggestion! We have made a detailed response to this question in R5 of Response To Meta-reviewer. Please see R5 for details.

%%%%%%%%%%%%%%%%%%%%%% W4 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{The authors have reported the peak memory usage of index construction only.
			They are also recommended to report the peak memory usage of query processing.}
	\end{weakness}
}

\noindent
\textbf{Response:} 
Thank you for your suggestion! We have made a detailed response to this question in R6 of Response To Meta-reviewer. Please see R6 for details.

### 2025-07-21 Revision/response.tex

To further enrich the complexity of multi-modal queries, we additionally selected 500,000 text vectors and 500,000 image vectors to form a mixed base dataset, and we similarly selected 5,000 text vectors and 5,000 image vectors as query vectors. We then conducted both attribute filtering and range queries on this multi-modal dataset by combining text and image queries. This allows us to further analyze the robustness of the algorithms. The related experimental results are presented in the Multi-modal Queries sections of Section 4.2.4 and Section 4.3.4.

As for complex query types involving both attribute and range filters, to the best of our knowledge, there is currently no ANN algorithm (except for general-purpose systems like Milvus and Faiss) that can support both types of filtering simultaneously. For example, ACORN needs to build separate indices for each scenario and cannot support attribute and range filtering at the same time. Therefore, in our study, we chose to consider these query types separately, rather than jointly.

%%%%%%%%%%%%%%%%%%%%%% R4 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Instead of using the point ID, run experiments with meaningful attributes for RF-NN search on datasets (Deep, YT-Audio, WIT).}
	\end{metarevision}
}

\noindent
\textbf{Response:} 
Thank you for your suggestion. Using IDs as attributes for range filtering is a prevalent method in current range filtering algorithm evaluations, which indeed has considerable limitations. To address this issue, we have added two datasets that use real attributes:

\textbf{YT-Audio-Real dataset:} For this dataset, we utilized the URLs provided by the YouTube8M dataset to crawl corresponding video category IDs and view counts as real attributes, and used view counts as the attribute for range filtering experiments.

\textbf{WIT-Real dataset:} We used the \texttt{clip-vit-base-patch32} model to encode the \texttt{page\_title} field from the WIT dataset into vectors, and extracted the language type and the length of the \texttt{context\_page\_description} field as real attributes, and used them for range filtering.
%%%%%%%%%%%%%%%%%%%%%% R5 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Evaluate if the server setting affects the relative ordering of methods in experiments}
	\end{metarevision}
}

@@

\noindent
\textbf{Response:} We think this is an excellent suggestion. We have enhanced our experiments by incorporating more complex multimodal dataset evaluations in Section \textcolor{blue}{XXX} of the paper. Initially, our paper utilized the Text2Image dataset, which is commonly used in existing multimodal ANN algorithms. This dataset presents a modality gap, as the base vectors are images while the query set consists of text, often requiring algorithms to exhibit stronger robustness for good performance. To further enrich the evaluation of complex multimodal queries, we selected 500,000 text vectors and 500,000 image vectors from the Text2Image dataset to form a mixed base query dataset. Similarly, we chose 5,000 image vectors and 5,000 text vectors as query vectors, combining both text and image modalities. We then performed attribute filtering and range queries on this multimodal dataset to further analyze algorithm robustness.  The relevant experimental results are presented and discussed in Section\textcolor{blue}{XXX}of our paper.

\section*{Response to Review 2}
\setcounter{weakness}{0}

%%%%%%%%%%%%%%%%%%%%%% W1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{In the experimental study, datasets did not originate from the real applications for hybrid queries.
			Regarding the datasets for AF-NN search (Msong, Audio, SIFT1M, GIST1M, GloVe, Enron),
			the attributes were generated synthetically but not real.
			Regarding the datasets for RF-NN search (Deep, YT-Audio, WIT), the data point ID was used as attribute;
			however, it is not meaningful to issue range query on data point ID.
			In order to match with the introduction, the authors are recommended to
			include a real dataset from e-commerce platform with both vectors and attributes.
		}
	\end{weakness}
}

\noindent
\textbf{Response:} 
Thank you for your suggestion. We fully understand your concern regarding the use of synthetic or less meaningful attributes in our hybrid query experimental setup.

To address this crucial issue and enhance the real-world relevance of our evaluation, we have added two new real-world datasets with genuine attributes to our attribute filtering and range query experiments, as detailed in MetaReview R3.

By incorporating the YT-Audio-Real and WIT-Real datasets with their respective real attributes, we believe our experimental study now better reflects real-world application scenarios, and, as you suggested, allows for a more comprehensive and meaningful evaluation of hybrid query functionality.

@@

\noindent
\textbf{Response:} 
Thank you for your suggestion.
We conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset.
The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the lower CPU frequency of the Xeon 6330 processors.

\textcolor{blue}{"We conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12(b). Compared with the experimental results on the original server (as shown in Figure 4d), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency of the Xeon 6330 compared to the original server, the QPS values are slightly lower across all methods."}
%%%%%%%%%%%%%%%%%%%%%% W3 %%%%%%%%%%%%%%%%%%%%%%

\myfbox{
	\begin{weakness}
		\textit{In the experimental setup, it is unclear whether data storage (disk or SSD) is used.
			In Table 1, please clarify which methods are disk-based, and which methods are memory-based.
			For disk-based methods, it is also meaningful to report the cost breakdown (e.g., in terms of I/O time and CPU time).}
	\end{weakness}
}

\noindent
\textbf{Response:} 
Thank you for your suggestion! Currently, most hybrid query methods are based on memory, except for filteredDiskANN, which supports SSD, so we will add explanation information in the paper. At the same time, we also use real data sets to compare the difference in search performance between filteredDiskANN in memory and on SSD. The results are shown in Figure \ref{fig:recall-latency}:
\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{fig/recall_latency_all.png}
	\caption{}
	\label{fig:recall-latency}
\end{figure}

 In response to your request for a breakdown of I/O and CPU cost in disk-based methods, we conducted additional experiments on the real-world yt8m dataset. We compared three variants of DiskANN:

### 2025-07-21 VLDB2026/main.tex

		\setlength{\textfloatsep}{0.1cm}
		\caption{Comparison of RF-ANN search algorithms}
		\small	% 只会影响当前组的内容
		\label{tab:range_algo}
		\begin{tabular}{|c|c|c|c|}
			\hline
			\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
			\hline
			DSG & Graph & Y & N \\
			iRange & Graph & N & Y \\
			SeRF & Graph & Y & Y \\
			UNIFY & Graph & Y & Y \\
			WinFilter & Graph & N & Y  \\
			\hline
		\end{tabular}

		\footnotesize{
			\begin{minipage}{\linewidth}
				\centering
				The indicators are consistent with those in Table ~\ref{tab:compair_1}.
				%				\textsuperscript{Y} Support, 
				%				\textsuperscript{N} Unsupport.
				%				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
				%				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
				%				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
			\end{minipage}

		}

	\end{table}

@@

	We introduce 5 representative range filtering algorithms and present a comparative overview in Table~\ref{tab:range_algo}.

@@

	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Attribution}}

@@

	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Range}}

>>>>

%	\renewcommand{\arraystretch}{0.9}
%	\begin{table}[t]
%		\centering
%		
%		\setlength{\textfloatsep}{0.1cm}
%		\caption{Comparison of RF-ANN search algorithms}
%		\small	% 只会影响当前组的内容
%		\label{tab:range_algo}
%		\begin{tabular}{|c|c|c|c|}
%			\hline
%			\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
%			\hline
%			DSG & Graph & Y & N \\
%			iRange & Graph & N & Y \\
%			SeRF & Graph & Y & Y \\
%			UNIFY & Graph & Y & Y \\
%			WinFilter & Graph & N & Y  \\
%			\hline
%		\end{tabular}
%		
%		
%		\footnotesize{
%			\begin{minipage}{\linewidth}
%				\centering
%				The indicators are consistent with those in Table ~\ref{tab:compair_1}.
%				%				\textsuperscript{Y} Support, 
%				%				\textsuperscript{N} Unsupport.
%				%				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
%				%				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
%				%				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
%			\end{minipage} 
%			
%		}
%		
%	\end{table}

@@

	We introduce 5 representative range filtering algorithms and present a comparative overview in \textcolor{orange}{Table~\ref{tab:compair_1}.}

@@

%	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Attribution}}

@@

%	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Range}}
